Milestone 2: Datasets Generation

### 2019-10-22 perf_release_criteria/milestone_3/ms_2_dataset_generation.Rmd
Moving bootstrap creation to this notebook.

df_train <- load_df('../data/milestone2/df_pd_67.csv')
df_validate <- load_df('../data/milestone2/df_pd_68.csv')
```

@@

```{r serialize_dataset}
image_file_path <- paste('data/milestone2/df_train_validate_', format(Sys.time(), "%Y%m%d"), '.RData', sep='')
save(df_train_f, df_validate_f, bts.1x, bts.4x, bts.8x, bts.16x,
     file = image_file_path)
```

Then push the results to GCP in the `moz-fx-dev-subbeta` bucket, under `r image_file_path`.

@@

upload_try <- gcs_upload(image_file_path, name = image_file_path)
upload_try
```

>>>>

df_train <- load_df('data/df_pd_67.csv')
df_validate <- load_df('data/df_pd_68.csv')
```

@@

```{r serialize_dataset}
image_file_name <- paste('df_train_validate_', format(Sys.time(), "%Y%m%d"), '.RData', sep='')
image_file_path <- file.path('data', image_file_name)
save(df_train_f, df_validate_f, bts.1x, bts.4x, bts.8x, bts.16x,
     file = image_file_path)

gcs_file_path <- file.path('data', 'milestone2', image_file_name)
```

Then push the results to GCP in the `moz-fx-dev-subbeta` bucket, under `r gcs_file_path`.

@@

upload_try <- gcs_upload(image_file_path, name = gcs_file_path)
upload_try
```
